A meta-analysis of fungicide effects on mungbean powdery mildew

### 2021-05-27 04_Severity_MetaAnalysis.Rmd
Capitalise sentances

disease_estimates_table <-
   flextable(results_mv[c(2,5,6,3,4), ]) %>%
   align(j = 2:10, align = "center", part = "all") %>%
   fontsize(size = 8, part = "body") %>%
   fontsize(size = 10, part = "header") %>%
   italic(italic = TRUE, part = "header") %>%
   set_caption(
      "Table 3: Estimated powdery mildew severity for each spray schedule treatment. Estimates were back transformed using a inverse logit from the network meta-analysis of data obtained from grey literature reports of (k) field trials undertaken in Eastern Australia. P values indicate statistical significance in comparison to the intercept."
   ) %>%
   autofit() %>%
   footnote(
      i = 1,
      j = c(2:4,7:12),
      value = as_paragraph(
         c(
            "number of treatment means categorised to each spray schedule",
            "number of trials with the respective spray schedule",
            "estimated mean disease severity",
            "indicates the significance between each respective spray schedule and the no spray control (intercept)",
            "Lower range of the 95% confidence interval",
            "Upper range of the 95% confidence interval",
            "Fungicide spray schedule percent efficacy",
            "Lower range of the 95% confidence interval",
            "Upper range of the 95% confidence interval"
         )
      ),
      ref_symbols = letters[c(1:7,4,5)],
      part = "header",
      inline = TRUE
   )%>%
   add_header(Moderator = "",
              N = "",
              k = "",
              mu = "Effect Size",
              se = "Effect Size",
              Z = "Effect Size",
              `CI_{L}` = "Effect Size",
              `CI_{U}` = "Effect Size",
              P  = "Effect Size",
              Efficacy = "PM control",
              `Eff CI_lower` = "PM control",
              `Eff CI upper` = "PM control") %>%
   merge_h( part = "header")%>%
   hline_top(part="all", border = officer::fp_border(color = "black", width = 2) )

>>>>

disease_estimates_table <-
   flextable(results_mv[c(2,5,6,3,4), ]) %>%
   align(j = 2:10, align = "center", part = "all") %>%
   fontsize(size = 8, part = "body") %>%
   fontsize(size = 10, part = "header") %>%
   italic(italic = TRUE, part = "header") %>%
   set_caption(
      "Table 3: Estimated powdery mildew severity for each spray schedule treatment. Estimates were back transformed using a inverse logit from the network meta-analysis of data obtained from grey literature reports of (k) field trials undertaken in Eastern Australia. P values indicate statistical significance in comparison to the intercept."
   ) %>%
   autofit() %>%
   footnote(
      i = 1,
      j = c(2:4,7:12),
      value = as_paragraph(
         c(
            "Number of treatment means categorised to each spray schedule",
            "Number of trials with the respective spray schedule",
            "Estimated mean disease severity",
            "Indicates the significance between each respective spray schedule and the no spray control (intercept)",
            "Lower range of the 95% confidence interval",
            "Upper range of the 95% confidence interval",
            "Fungicide spray schedule percent efficacy",
            "Lower range of the 95% confidence interval",
            "Upper range of the 95% confidence interval"
         )
      ),
      ref_symbols = letters[c(1:7,4,5)],
      part = "header",
      inline = TRUE
   )%>%
   add_header(Moderator = "",
              N = "",
              k = "",
              mu = "Effect Size",
              se = "Effect Size",
              Z = "Effect Size",
              `CI_{L}` = "Effect Size",
              `CI_{U}` = "Effect Size",
              P  = "Effect Size",
              Efficacy = "PM control",
              `Eff CI_lower` = "PM control",
              `Eff CI upper` = "PM control") %>%
   merge_h( part = "header")%>%
   hline_top(part="all", border = officer::fp_border(color = "black", width = 2) )
